Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-30 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

![**Figure `r fig_ecosystem`.** Vertical partitioning of (a) evapotranspiration and (b) C fluxes in tropical forests. Panel (a) is from @kunertRevisedHydrologicalModel2017; panel (b) presents averages for 14 tropical forests from @piponiot_sizerelated_inreview.](schematics/ecosystem vertical partitioning/ecosystem partitioning.png)

>>>>

![**Figure `r fig_ecosystem`. Vertical partitioning of (a) evapotranspiration and (b) C fluxes in tropical forests.** Panel (a) is from @kunertRevisedHydrologicalModel2017; panel (b) presents averages for 14 tropical forests from @piponiot_sizerelated_inreview.](schematics/ecosystem vertical partitioning/ecosystem partitioning.png)
